### 2018-03-09 README.Rmd
Add more details to README

#Infer

@@

@@

@@

Hypothesis test for a difference in proportions:

@@

Confidence interval for a difference in means:

```{r}
mtcars %>%
  specify(mpg ~ am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("1", "0"))
```

>>>>

# Infer

@@

<!--figs/infer.svg-->
<!--http://www.r-pkg.org/badges/version/infer-->
<!--figs/master.svg-->
<!--https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg-->

@@

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first:

```{r}
install.packages("remotes")
remotes::install_github("andrewpbray/infer", ref = "develop")
```

To see the things we are working on with the package as vignettes/Articles, check out 
the developmental `pkgdown` site at <https://infer-dev.netlify.com>.

### Contributing

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
use the package.

@@

Hypothesis test for a difference in proportions (using the formula interface 
`y ~ x` in `specify()`):

@@

Confidence interval for a difference in means (using the non-formula interface
giving both the `response` and `explanatory` variables in `specify()`):

```{r}
mtcars %>%
  specify(response = mpg, explanatory = am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("1", "0"))
```

Note that the formula and non-formula interfaces work for all implemented inference
procedures in `infer`. Use whatever is more natural for you. If you will be doing
modeling using functions like `lm()` and `glm()`, we recommend you begin to use the
formula `y ~ x` notation as soon as possible though.
